True Lies

### 2019-02-27 response-to-reviewers.Rmd

---
title: "Untitled"
author: "David Hugh-Jones"
date: "27/02/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

> The most obvious comment that both reviewers made is one of etiquette: you are unnecessarily harsh
> to GSV! I would like you to reframe the discussion of GSV following the suggestions of R2. (And yes,
> the “don’t use the GSV method” in the conclusion should be replaced with something more informative
> and less pedantic.)

[TODO]

> I also like R2’s suggestion about either providing power calculations (see the example table this
> reviewer provided) and/or an online calculator that you will discuss in your paper. Finally, please
> ensure that you address R1’s comments on clarity.

[Already in software]

* Reviewer 1

> I think that the statistical argument could be explained more clearly... I would encourage the 
> author to expand this part of the paper to explain things more clearly.

[Use bits of R1's example]

I also think that it would be important to explain more clearly how the statistical and conceptual arguments relate to the lack of nominal coverage of the estimator and its biasedness. This is not very clear at the moment - I am referring in particular to the last four paragraphs of page 4. In particular, I struggle to see how the two arguments can help explain the poor nominal coverage of the GSV method. In those paragraphs, it would also be useful to make a clearer distinction between the GSV method as an estimator of the proportion of lies actually told in the sample ("Lies") - and the problems that arise there; and the method as an estimate of the proportion of liars in the sample ("lambda"). At the moment the paper goes back and forth between the problems that arise in either case, which is confusing.

This is also true in the following sections ("Alternative methods" and "Point estimates"). As far as I understand, the exercise here consists in comparing across methods the coverage and point estimates of lambda (this is confusingly referred to as "Liars" in this part of the paper). It would be useful to point this out more clearly.

I also thought that the part on "empirical Bayes" is not very well explained. Indeed, I wondered whether the inclusion of this section may detract from the overall value of the paper, since it becomes slightly less focused. The same goes for table 9 and corresponding text in the paper - it seems that this goes somewhat beyond the scope of the paper - which in my opinion works best as a comment focused on the GSV method, rather than its applications in subsequent papers.

Regarding the conclusions, I liked the prescriptive approach of the paper. However, I think that the first precept, "Do not use the GSV method", is perhaps too strong. I think that the simulations presented in the paper convinced me that GSV is not a good method to estimate the proportion of liars ("lambda"), espcially in comparison with the alternative methods - but I am less convinced that the method is a terrible estimator of the proportion of lies actually told in the sample ("Lies"). The simulations in the Appendix do not seem to show a very large bias or dramatic drops in coverage in this case. So, in my view, the first precept could perhaps be rephrased as "Do not use the GSV method if you are interested in estimating the proportion of liars in your sample".

I also liked the thought experiment presented in the concluding section. However, one important point to make here is that, in such an experiment, each subject would face a different truthful distribution (and the experiment would not be able to control or observe which subject faced which distribution). We know from existing research that the underlying distribution matters for the willingness to lie. So this is a caveat to keep in mind when estimating the proportion of lies via this method.

Finally, I have some additional minor comments:
- p. 1, footnote 1: the acronym GSV is used before it has been explained
- p. 4: line 33, equation 1 should contain R/N, not R.
- p. 4, table 3: what does "Percentage of cases" mean?
- Figure 3 in the Appendix, the horizontal axis is missing

* Reviewer 2

Power Calculations: I believe one area that would be extremely useful for future research would be to provide some power calculations based on your proposed method (either frequentist or Bayesian).

[Give example in main paper]

Online Calculator: Another way the paper could be extremely valuable for future researchers would be, like GSV, to provide an online lying calculator so that researchers can easily use your improved method. I worry otherwise that while readers might find your paper interesting, if it is not trivial to apply (which I suspect will be the case for many), then they might not use your method. I will leave it up to you, but either a stand- alone piece of software, or possibly even a STATA routine if that is possible (which I would think would be preferable). In any case, I believe this would be an enormous improvement to the value of your paper (and citations).

[Maybe turn stuff into R package? Or just put some examples into the main paper.]

Suggested experiment in the concluding section: While I like the objective of the suggested experiment, I do not think the design works as I think it changes the nature/implication of lying...
in the second experiment, if a subject gets the white ball but lies and reports black, then there is only one outcome for the experiment: both subjects will report black, and it will be with certainty that the experimenter will know one of the subjects will have lied. This seems like it a potentially important difference that could affect the willingness of subjects to lie. Having more subjects in the room does not change the basic point that in your proposed setup that any subject that lies will make it clear to the experimenter that someone is lying, whereas in the current approach one subject lying does not guarantee the experimenter will detect lying. I see no way to avoid this without some form of deception.

[It's a fair point. Even if the number of white balls is unknown, subjects know the experimenter
knows. But, in a large session, this is perhaps not a big issue.
Acknowledge this point in a footnote. But, still worth making the suggestion.]

Tone down the negative attention to GSV, and get directly to your solution. Your method is the critical contribution, and make it central. Comparisons of the CIs in the simulations make this immediately clear. As I mentioned above, I believe that GSV made an important contribution by pointing out the lack of a good statistical inference method for estimating the distribution of lying in the literature, and your contribution is an obvious advance that gets the CIs to be essentially what we would expect. Hopefully, researchers in this literature will adopt an appropriate statistical inference. The likely two most important practical contributions from GSV is quite notably extended here: many studies likely have been under-powered to find significant differences, and closely related, many null results could thus likely be due to low power. Addressing my first two recommendations above (power and a calculator) will help the literature not fall prey to these mistakes.

[TODO. Maybe have less on GSV.]

### 2019-03-01 GSV-comment-brief.Rmd
Edits in response to reviewers

> **Abstract**: Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability
> distribution of the proportion of lies told in "coin flip" style experiments. I show that their
> estimates and confidence intervals are flawed. I demonstrate two better ways to estimate the 
> probability distribution of what we are really interested in: the proportion of liars.

@@

library(tufte)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tufte'))
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(echo = FALSE)
options(huxtable.knitr_output_format = "latex")

@@

Some people are honest, while others are likely to lie whenever it benefits them. We would like to understand
the prevalence of lying, because dishonesty may be economically and socially harmful. Since we
cannot simply ask people if they are liars, one way to estimate the proportion of liars in a group
is to ask them to report the result of a coin flip or other random device, offering them a payment
if they report heads. Liars don't always lie: they only lie when it benefits them. So they always
report heads irrespective of the true coin flip. ^[GSV maintain this assumption and so shall I.] If
there are many more heads than we would expect by chance, we can assume many people are lying. But
how many?

@@

Table 3 of GSV reports Monte Carlo simulations, which show that the probability of a Type II error
can be up to 50 per cent. GSV define a Type II error as the 95% confidence interval not containing
the true value. A 95% confidence interval which only contains the true value 50% of the time
is unusual. What is going on?

@@

I ran simulations to check the overall performance of the GSV confidence intervals. Simulations
parameters are shown in Table \ref{tab:params-table}. For each parameter combination, I ran 1000
simulations. $\lambda$ is the probability that an individual in the sample lies and report heads
when they observe tails:

\begin{equation}
\label{eqn:lambda}
\lambda = \textrm{Prob}(i \textrm{ reports heads}|i\textrm{ saw tails}).
\end{equation}

For each simulation and confidence interval, I computed whether the confidence interval contained
the true value of $\lambda$. Table \ref{tab:coverage-just-gsv} shows the results.

@@

```{r coverage-overall}

@@

ht_just_gsv <- ht_overall[1:2,]
label(ht_just_gsv) <- "tab:coverage-just-gsv"
ht_just_gsv[1, 1] <- ""
theme_plain(ht_just_gsv)
```

By definition, 95% of 95% confidence intervals ought to contain the true value, on average. This is
called "achieving nominal coverage". GSV intervals are far from this. The confidence intervals are
too narrow. This problem holds across all simulated probabilities of the low outcome, confidence
levels, and sample sizes.^[See the appendix.]

Why does this happen? We can get a clue by running the GSV method when there are 10 reports of
"heads" out of 10 for a fair coin flip (*R = N = 10, P = 0.5*). The resulting point estimate is that
100% of subjects lied. The upper and lower 99% confidence intervals are also 100%. Naïvely, this
might seem wrong. Can we rule out that 8 subjects lied, and the two honest subjects both saw heads?

In fact, the GSV method works like this. First, given *R* reports of heads, the probability that a
total of *T* "true" heads were observed is calculated as:

\begin{equation}
\label{eqn:truncated-binom}
\textrm{Prob}(T \textrm{ heads}| R; N, P) = \frac{
  \textrm{binom}(T,N, 1 - P)
}{
  \sum^R_{k=0}\textrm{binom}(k,N, 1 - P)
}
\end{equation}

@@

\begin{equation}
\textit{Lies} = \frac{R-T}{N-T} 
\end{equation}

because $N - T$ people saw the low outcome and had the chance to lie. Combining this
with the truncated binomial gives a cumulative distribution function of the proportion of liars.
This is then used to estimate means and confidence intervals.

Putting these together, for $R = N = 10$, the estimated distribution of liars is calculated as follows:

@@

There are two problems with this approach. One is statistical, one is conceptual.

@@

First, if 10 out of 10 heads are reported, you should learn two things. On the one hand, there are
probably many liars in your sample. On the other hand, probably a lot of coins really landed heads.
The probability distribution in equation (\ref{eqn:truncated-binom}) does not take account of this.
In particular, for *R = N*, it reduces to the binomial distribution. This is not correct. For
example, in my simulations with $P = 0.5$, the overall probability that there were 10 heads when $R
= N = 10$ was about 1 in `r inv_prob_h`, not 1 in 1024. When $\lambda = 0.2$, it was about 1 in 
`r inv_prob_h_l20`. The same is true at the other end of the scale: when *R* is low, we indeed learn
that $T \le R$ but also that the overall distribution is not shaped like the prior.

Second, more importantly, the GSV approach estimates *Lies*, the distribution of the proportion of 
*lies actually told*, among the subsample of people who saw tails. But we are not usually interested
in the proportion of lies actually told. We care about the probability that people in the
sample would lie if they saw tails --  $\lambda$ in equation (\ref{eqn:lambda}). This $\lambda$ can
be interpreted in different ways. It could be that on seeing a tail, each person in the sample lies
with probability $\lambda$. Or it could be that the sample is drawn from a population of whom
$\lambda$ are (always) liars, and $1 - \lambda$ are truth-tellers. *Lies*, on the other hand,
has no interpretation in the population, because the rest of the population has no chance to tell a lie
in the experiment. Indeed, when GSV run Monte Carlo simulations, they themselves check their
confidence intervals against $\lambda$ (which they call $Q$).

The fact that some people saw heads, and had no reason to lie, is just a nuisance for estimation.
Similarly, we are not interested, per se, in whether more lies were actually told in one group than
another. Suppose that 9 out of 10 people saw heads. Only one person had a reason to lie, so by
definition, *Lies* will be either 0 or 1. This will almost certainly be different from the value of
*Lies* in another group where there were fewer heads. But that tells us very little, either about the 
samples as a whole, or about the population they come from.

*Lies* can be treated as an estimate of $\lambda$. It is unbiased: it is an estimate of 
$\lambda$ in the random sample of $N - T$ people who saw tails. But it can be a very noisy estimate. 
Again, suppose 10 heads out of 10 are reported, and 9 heads were really observed. *Lies* is 100%. 
But it is 100% of just one person.

The first of these two problems means that the GSV distribution of *Lies* is wrong. In the appendix
I show that their estimator can have substantial bias. In fact, it performs worse than the naïve
estimator from equation (\ref{eqn:naive-estimator}), $\frac{R-(1-P)}{P}$. Since the true value of
*Lies* is an unbiased estimator of $\lambda$, the GSV estimator is also a biased estimator of
$\lambda$, as we will see. Also, the GSV confidence intervals do not always achieve nominal coverage
of *Lies*. When the number of heads reported is either high or low, the percentage of confidence
intervals containing *Lies* may fall below the nominal value.

The second problem means that the GSV confidence intervals are not correct for $\lambda$. We can
tell that the second problem matters, because the confidence interval coverage of $\lambda$ is much
worse than coverage of *Lies*.

@@

The problem is especially bad when there are many reports of heads. In this case there were probably
many true heads, so *T* is high and the true sample size $N - T$ is low. Table \ref{tab:coverage-rn}
shows this. It splits the simulations by the proportion of reported heads, *R/N*. Coverage levels
fall off sharply as *R/N* increases. For fair coin flips, *R/N* is typically greater than
0.5, in the simulations and in reality.

```{r coverage-rn}
coverage_rn <- sim_est %>% 
      filter(method=="gsv") %>% 
      group_by(
        `R/N:` = factor(Hmisc::cut2(R/N, cuts = c(0, 1/4, 1/2, 3/4, 1)))      
      ) %>% 
      mutate(pct_cases = n()/nrow(.)) %>% 
      group_by(`R/N:`, CI) %>% 
      summarize(
        mean_in_ci  = mean(within_ci, na.rm = TRUE), 
        `Percentage of cases` = pct_cases[1]
      ) %>% 
      mutate(CI = paste0("CI ", CI, "%")) %>% 
      spread(CI, mean_in_ci)

as_huxtable(coverage_rn, add_colnames = TRUE) %>% 
      set_caption("GSV confidence interval coverage by proportion of heads reported ($R/N$)") %>% 
      set_label("tab:coverage-rn") %>% 
      set_escape_contents(2:3, 1, FALSE) %>% 
      set_number_format(-1, -1, list(pct_format)) %>% 
      theme_plain() %>% 
      set_right_border(-1, 2, 0.4)
```

# Alternative methods

Can we do better? Start with the probability of getting *R* reports of heads in total, given
$\lambda$. Since individuals report heads either if they see heads with probability $1-P$, or if
they see tails but lie, with probability $\lambda P$, this is just:

\begin{equation}
\textrm{Pr}(R|\lambda; N,P) = \textrm{binom}(R, N, (1 - P) + \lambda P)
\end{equation}

That immediately suggests the first method, which is to estimate the parameter of this distribution,
$(1 - P) + \lambda P$, from the proportion of heads reported in the sample, then back out $\lambda$.
This is the conventional method of e.g. @abeler2016preferences. It is justified if the sample is
large, because this will lessen sampling variation in the proportion of actual heads observed.
Similarly, if the sample is large enough, we can generate hypothesis tests for a value of $\lambda$
-- e.g., zero -- by using the tails of the binomial distribution. And we can back out confidence
bounds for $\lambda$ from confidence bounds for the population proportion of heads reported in the
same way. As GSV point out, in small samples, this method runs the risk that the sample proportion
of high outcomes will be different from its expected value.^[In particular, this method can estimate
confidence bounds for $\lambda$ lower than 0. If so, we can set them to 0.]   We'll see whether this
matters.

There are numerous ways to calculate confidence intervals in a test of proportions. See e.g.
@agresti1998approximate. Here, I use the binomial exact test of @clopper1934use, which is 
known to be conservative. I call this the "frequentist" method.

The second method is to use Bayes' rule. Start with a prior probability density function over
the probability of liars, $\phi(\lambda)$. The posterior probability is then:

\begin{equation}
\phi(\lambda | R; N,P) = \frac{
  \textrm{Pr}(R|\lambda; N,P) \phi(\lambda)
}{
  \int_0^1 \textrm{Pr}(R|\lambda'; N,P) \phi(\lambda) \; \textrm{d}\lambda
}
\end{equation}

From this, one can derive confidence intervals and expected values in the usual way.^[R code to do
this is available at https://github.com/hughjonesd/GSV-comment. ] Technically, they are Bayesian
"credible" intervals. I use Highest Posterior Density intervals [@hyndman1996computing], rather than
the central confidence interval. This allows the intervals to include endpoints of the distribution,
which is important when e.g. testing for $\lambda = 0$.

I ran these estimation methods on my simulated data. Results are shown in Table
\ref{tab:coverage-allmethods}. Both frequentist and  Bayesian methods mostly achieve the nominal
confidence level, with more than 90/95/99% of intervals containing the true value of *Liars*. The
exception is the frequentist 99% confidence interval, which is too narrow.

```{r coverage-allmethods}
ht_overall %>% 
      set_caption("Coverage levels for GSV and alternative methods") %>% 
      set_label("tab:coverage-allmethods")
```

Frequentist confidence intervals could be less accurate when N is low, since that leads to more
sampling variation in the number of true heads. Table \ref{tab:coverage-N} checks this by looking
separately at simulations with *N = 10* and *N = 50*. Frequentist 99% confidence intervals indeed
appear slightly too narrow for this range. Bayesian confidence intervals are fine. Both alternatives
perform much better than the GSV approach.

@benndorf2017experienced use the GSV method to calculate confidence intervals for the proportion of
liars in a lying task with a die roll ($P = 5/6$). From 57 reports of the best outcome, out of 98
subjects, they calculate a lying rate of 49.68%, with a 95% CI of (45.3%, 53.95%). Using the
Bayesian method with a uniform prior, the confidence interval becomes (`r bennd_bounds[1]`, 
`r bennd_bounds[2]`), about twice as big. Obviously, this matters for e.g. sample size calculations.

@@

We can also compare the accuracy of point estimates of *Liars*. Table \ref{tab:bias} shows bias
(the estimated value minus the true value of $\lambda$) for different methods by different *N*.
The Bayesian method is always the least biased until $N = 500$, and the GSV method is the most biased.

@@

The Bayesian method might have an advantage here, since it assumes a uniform prior and the
simulations indeed used a uniform distribution of the proportion of liars *L/N*. In fact, further
analysis reveals that the Bayesian method is best across all specific values of *L/N* up to
80%.^[When *L/N = 1*, all subjects deterministically report heads, and both Frequentist and
Bayesian point estimates are exactly correct.] So, the Bayesian method is likely to be best unless
one is sure that the true *L/N* is rather high.

@@

# Power tests

```{r power-tests}
power_l_25 <- power_calc(N = 100, P = 0.5, lambda = 0.25)
power_l_10 <- power_calc(N = 100, P = 0.5, lambda = 0.10)
```

GSV argue that existing sample sizes may be too small to reject "no lying" ($\lambda = 0$). 
We can check this with the Bayesian method by simulations. With a uniform prior and an $N$ of 100, 
the Bayesian method has `r pct_format(power_l_25)` power to detect $\lambda$ of 25% and 
`r pct_format(power_l_10)` power to detect $\lambda$ of 10%. So, on this we agree.

# Empirical Bayes

@@

```{r hj-data}

load("honesty.RData")
dfr <- dfr %>% 
      filter(heads %in% 1:2, ! is.na(resnat) , age %in% 2:6)

nats <- dfr %>%  
      group_by(resnat) %>% 
      summarize(
        heads = sum(heads==1), 
        N = n(),
        prop_heads = heads/N,
        prop_liars = 2*prop_heads - 1
      )

pp <- suppressWarnings(MASS::fitdistr(nats$prop_liars, "beta", start = list(
        shape1 = 1, shape2 = 1
      )))
pooled_prior <- function (x) dbeta(x, pp$estimate["shape1"], pp$estimate["shape2"])

distribs <- apply(nats[, c("heads", "N")], 1, function (r) {
  N <- r["N"]
  update_prior(
      heads = r["heads"],
      N = N,
      P = 0.5, 
      prior = pooled_prior
  )
})

names(distribs) <- nats$resnat

nat_means <- sapply(distribs, dist_mean)
nat_cis <- sapply(distribs, dist_hdr, conf_level = 0.95)
rownames(nat_cis) <- c("ci.low", "ci.high")

nats <- cbind(nats, t(nat_cis), mean = nat_means)

nats %<>% arrange(mean)

# nats$resnat <- factor(nats$resnat, levels = nats$resnat)
```

For example, @hugh2016honesty estimates the dishonesty rates of 15 nations using a coin flip
experiment. We can fit a beta distribution using the 15 observations of *2R/N - 1*. This will be
our prior.

```{r hj2016-pic, fig.cap = "Posterior means and confidence intervals for proportion dishonest in 15 countries. Crosses are naïve estimates.", fig.align="center", fig.width=5.5, fig.height=4}

ggplot(nats, aes(x = factor(resnat, levels = resnat), y = mean, fill = mean)) +
      geom_col(alpha = 0.8) +
      geom_linerange(aes(ymin = ci.low,ymax = ci.high)) +
      geom_point(aes(y = prop_liars), shape = 4, size = 3, colour = "red") +
      xlab("Nation") + ylab("Prop. liars") +
      scale_fill_viridis_c(option = "A", guide = "none") + 
      theme_light()+
      coord_flip()

Results are shown in Figure \ref{fig:hj2016-pic}, with means and 95% confidence intervals. There is
some "shrinkage" towards the pooled mean from the naïve per-country estimates found by calculating
*2R/N - 1* separately for each country). One of the strengths of empirical Bayes,  as
@casella1985introduction points out, is that it "anticipates regression to the mean". That is, as
there is noise in the data, the most and least honest groups in the data probably had some extreme
error terms. So the British people in the sample may be less honest, and the Chinese people more
honest, than the per-group data suggest.

# Bayesian hypothesis testing

>>>>

> **Abstract**: Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability
> distribution of the proportion of lies told in "coin flip" style experiments. I show that their
> estimates and confidence intervals are flawed. I demonstrate two better ways to estimate the 
> probability distribution of what we really care about -- the proportion of liars -- and
> I provide R software to do this.

@@

library(tufte)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tufte'), highlight = FALSE)
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(echo = FALSE)
options(huxtable.knitr_output_format = "latex")

@@

Some people are honest, while others are likely to lie whenever it benefits them. We would like to understand
the prevalence of lying, because dishonesty may be economically and socially harmful. Since we
cannot simply ask people if they are liars, one way to estimate the proportion of liars in a group
is to ask them to report the result of a coin flip or other random device, offering them a payment
if they report heads. Liars don't always lie: they only lie when it benefits them. So they always
report heads irrespective of the true coin flip. ^[@Garbarino2018 maintain this assumption and so shall I.] If
there are many more heads than we would expect by chance, we can assume many people are lying. But
how many?

@@

@@

I ran simulations to check the overall performance of the GSV confidence intervals. Simulations
parameters are shown in Table \ref{tab:params-table}. $\lambda$ is the probability that an individual in the sample lies and report heads
when they observe tails:

\begin{equation}
\label{eqn:lambda}
\lambda = \frac{1}{N} \sum_{i=1}^N \textrm{Prob}(i \textrm{ reports heads}|i\textrm{ saw tails}).
\end{equation}

For each parameter combination, I ran 1000 simulations, drawing random coin flips and reports given
$P$, $\lambda$ and $N$.

For each simulation and confidence level, I computed whether the GSV confidence interval contained
the true value of $\lambda$. The first row of Table \ref{tab:coverage-allmethods} shows the results.

@@

```{r coverage-allmethods}

@@

ht_overall %>% 
      set_caption("Coverage levels for GSV and alternative methods") %>% 
      set_label("tab:coverage-allmethods")

By definition, 95% of 95% confidence intervals ought to contain the true value, on average. This is
called "achieving nominal coverage". GSV confidence intervals are
too narrow.^[This problem holds across all simulated probabilities of the low outcome, confidence
levels, and sample sizes. See the appendix.]

To deal with this problem, I test two alternative methods for calculating confidence intervals
on my simulated data. The first ("Frequentist") is the standard method of deriving confidence intervals from a binomial test. The second is a Bayesian method.

To understand the statistics, start with the probability of getting *R* reports of heads in total, given
$\lambda$. Since individuals report heads either if they see heads with probability $1-P$, or if
they see tails but lie, with probability $\lambda P$, this is just:

\begin{equation}
\label{eqn:binom}
\textrm{Pr}(R|\lambda; N,P) = \textrm{binom}(R, N, (1 - P) + \lambda P)
\end{equation}

That immediately suggests the "Frequentist" method, which is to estimate the parameter of this
distribution, $(1 - P) + \lambda P$, from the proportion of heads reported in the sample, then back
out $\lambda$. This is the conventional method of e.g. @abeler2016preferences. It is justified if
the sample is large, because this will lessen sampling variation in the proportion of actual heads
observed. Similarly, if the sample is large enough, we can generate hypothesis tests for a value of
$\lambda$ -- e.g., zero -- by using the tails of the binomial distribution. And we can back out
confidence bounds for $\lambda$ from confidence bounds for the population proportion of heads
reported in the same way. As GSV point out, in small samples, this method runs the risk that the
sample proportion of high outcomes will be different from its expected value.^[In particular, this
method can estimate confidence bounds for $\lambda$ lower than 0. If so, we can set them to 0.]
We'll see whether this matters.

There are numerous ways to calculate confidence intervals in a test of proportions. See e.g.
@agresti1998approximate. Here, I use the binomial exact test of @clopper1934use, which is 
known to be conservative.

The second method uses Bayes' rule. Start with a prior probability density function over
$\lambda$, $\phi(\lambda)$. The posterior probability is then:

\begin{equation}
\label{eqn:bayes}
\phi(\lambda | R; N,P) = \frac{
  \textrm{Pr}(R|\lambda; N,P) \phi(\lambda)
}{
  \int_0^1 \textrm{Pr}(R|\lambda'; N,P) \phi(\lambda') \; \textrm{d}\lambda'
}
\end{equation}

From this, one can derive confidence intervals and expected values in the usual way. Technically,
they are Bayesian "credible" intervals. I used Highest Posterior Density intervals
[@hyndman1996computing], rather than the central confidence interval. This allows the intervals to
include endpoints of the distribution, which is important when e.g. testing for $\lambda = 0$.

Results in Table
\ref{tab:coverage-allmethods} show that both frequentist and  Bayesian methods mostly achieve the nominal
confidence level, with more than 90/95/99% of intervals containing the true value of *Liars*. The
exception is the frequentist 99% confidence interval, which is too narrow.

Frequentist confidence intervals could be less accurate when $N$ is low, since that leads to more
sampling variation in the number of true heads. Table \ref{tab:coverage-N} checks this by looking
separately at simulations with *N = 10* and *N = 50*. Frequentist 99% confidence intervals indeed
appear slightly too narrow for this range. Bayesian confidence intervals are fine.

# Understanding the GSV approach

Why does the GSV method produce narrow confidence intervals? We can get a clue by running the GSV method when there are 10 reports of
"heads" out of 10 for a fair coin flip (*R = N = 10, P = 0.5*). The resulting point estimate is that
100% of subjects lied. The upper and lower 99% confidence intervals are also 100%.

This is calculated as follows. First, given *R* reports of heads, the probability that a
total of $T$ "true" heads were observed is calculated as:

\begin{equation}
\label{eqn:truncated-binom}
\textrm{Prob}(T \textrm{ heads}| R; N, P) = \frac{
  \textrm{binom}(T, N, 1 - P)
}{
  \sum^R_{k=0}\textrm{binom}(k, N, 1 - P)
}
\end{equation}

@@

\begin{equation}
\label{eqn:lies}
\textit{Lies} = \frac{R-T}{N-T} 
\end{equation}

because $N - T$ people saw the low outcome and had the chance to lie. Combining this
with the truncated binomial gives a cumulative distribution function of *Lies*.
This is then used to estimate means and confidence intervals.

Putting these together, for $R = N = 10$, the estimated distribution of *Lies* is calculated as follows:

@@

There are two problems with this approach, one statistical, and one conceptual.

@@

First, if many heads are reported, you should learn two things. On the one hand, there are probably
many liars in your sample. On the other hand, probably a lot of coins really landed heads. The
probability distribution in equation (\ref{eqn:truncated-binom}) does not take account of this.

For example, suppose we are certain that everyone in the sample is a liar who always reports heads.
In this case, observing $R = N = 10$ gives us no information about the true number of heads. The
posterior probability that $T = 10$ is then indeed 1/1024, the same as the prior. Now suppose we
know that nobody in the sample is a liar. Then on observing $R = 10$, we are sure that there were
truly 10 heads: the posterior that $T = 10$ is 1. If exactly 5 out of 10 subjects are liars, then
observing $R = 10$ means that all 5 truth tellers really saw heads. The posterior probability that
$T = 10$ is then $1/32$, the chance that all 5 liars saw heads. And so on.

When we are uncertain about the number of liars, our posterior that $T = 10$ will be some weighted
combination of these beliefs. Unless we are certain everyone in the sample is a liar, the
probability that $T = 10$ will be greater than 1 in 1024. Equation (\ref{eqn:truncated-binom}) is
therefore not correct. In this case, it is equivalent to assuming that everybody in the sample is a liar,
whose report is uninformative about the true number of heads. One then uses the prior distribution
of heads to estimate the proportion of those who actually saw tails and lied.

Indeed, in the simulations with $P =
0.5$ and across all values of $\lambda$, the overall probability that there were 10 true heads,
conditional on $R = N = 10$, was about 1 in `r inv_prob_h`, not 1 in 1024. Fixing $\lambda = 0.2$,
it was about 1 in `r inv_prob_h_l20`.

This problem means that the GSV estimator of *Lies* is biased. In the appendix
I show that the GSV estimator can have substantial bias, and performs worse than the naïve
estimator from equation (\ref{eqn:naive-estimator}), $\frac{R/N-(1-P)}{P}$. Also, the GSV confidence intervals do not always achieve nominal coverage
of *Lies*. When the number of heads reported is either high or low, the percentage of confidence
intervals containing *Lies* may fall below the nominal value.

There is a second, more important problem. The GSV approach attempts to estimate *Lies* in equation
(\ref{eqn:lies}). This is the  proportion of *lies actually told*, among the subsample of people who
saw tails. But we are not usually interested in the proportion of lies actually told. We care about
the probability that a subject in the sample would lie if they saw tails --  $\lambda$ in equation
(\ref{eqn:lambda}). This $\lambda$ can be interpreted in different ways. Maybe on seeing a tail,
each person in the sample lies with probability $\lambda$. Or maybe the sample is drawn from a
population of whom $\lambda$ are (always) liars, and $1 - \lambda$ are truth-tellers. *Lies* has no
interpretation in the population, because the rest of the population has no chance to tell a lie in
the experiment.

*Lies* can be treated as an estimate of $\lambda$. It is unbiased: it estimates $\lambda$ from the
random, and randomly-sized, sample of $N - T$ people who saw tails. But it can be a very noisy
estimate. Again, suppose 10 heads out of 10 are reported, and 9 heads were really observed. *Lies*
is 100%. But it is 100% of just one person.

This means that even the correct confidence intervals for *Lies* would not be correct for $\lambda$.
For example, if 3 out of 3 subjects report heads, the GSV software reports a lower bound of 100% for
any confidence interval. Indeed, since anyone who had the opportunity to lie clearly did so, this is
the correct lower bound (if we arbitrarily define *Lies = 1* when $T = N$). But it
makes no sense as a confidence interval for $\lambda$: we clearly can't rule out that one or two
subjects truly saw heads, and would have reported tails if they had seen tails.

@@

Because of this problem, the GSV confidence interval coverage of $\lambda$ is much worse
than its coverage of *Lies*.The issue is especially serious when there are many reports of heads. In
this case there were probably many true heads, so *T* is high and the true sample size $N - T$ is
low, making *Lies* a noisy estimate of $\lambda$. Table \ref{tab:coverage-rn} shows this. It splits
the simulations by the proportion of reported heads, *R/N*. GSV coverage levels fall off sharply as
*R/N* increases. Note that for fair coin flips, *R/N* is usually greater than 0.5, both in the
simulations and in reality.

```{r coverage-rn}
coverage_rn <- sim_est %>% 
      filter(method=="gsv") %>% 
      group_by(
        `R/N` = factor(Hmisc::cut2(R/N, cuts = c(0, 1/4, 1/2, 3/4, 1)))      
      ) %>% 
      mutate(pct_cases = n()/nrow(.)) %>% 
      group_by(`R/N`, CI) %>% 
      summarize(
        mean_in_ci  = mean(within_ci, na.rm = TRUE), 
        `Percentage of simulations` = pct_cases[1]
      ) %>% 
      mutate(CI = paste0("CI ", CI, "%")) %>% 
      spread(CI, mean_in_ci)

as_huxtable(coverage_rn, add_colnames = TRUE) %>% 
      set_caption("GSV confidence interval coverage by proportion of heads reported ($R/N$)") %>% 
      set_label("tab:coverage-rn") %>% 
      set_escape_contents(2:3, 1, FALSE) %>% 
      set_number_format(-1, -1, list(pct_format)) %>% 
      theme_plain() %>% 
      set_right_border(-1, 2, 0.4) %>% 
      set_width(0.75)
```

@@

We can also compare the accuracy of point estimates of $\lambda$ between GSV, Frequentist and
Bayesian methods. Table \ref{tab:bias} shows bias (the estimated value minus the true value of
$\lambda$) for different methods by different *N*. The Bayesian method is always the least biased
until $N = 500$, and the GSV method is the most biased.

@@

The Bayesian method might have an advantage here, since it assumes a uniform prior and the
simulations indeed used a uniform distribution of the proportion of liars *L/N*. In fact, further
analysis reveals that the Bayesian method is best across all specific values of *L/N* up to
80%.^[When *L/N = 1*, all subjects deterministically report heads, and both Frequentist and
GSV point estimates are exactly correct.] So, the Bayesian method is likely to be best unless
one is sure that the true *L/N* is rather high.

@@

# Comparing different groups

@@

We can also test hypotheses using the Bayesian approach. If two samples are independent, then the 
probability that e.g. the true proportion of liars in sample 1 is smaller than in sample 2 can be
calculated from the posterior distributions for each sample:

\begin{equation}
\label{eqn:hypothesis-testing}
\int^1_0 \int_0^{\lambda_1} \phi(\lambda_1)\phi(\lambda_2) \; \mathrm{d}\lambda_2 \mathrm{d}\lambda_1
\end{equation}

# Applications

@benndorf2017experienced use the GSV method to calculate confidence intervals for the proportion of
liars in a lying task with a die roll ($P = 5/6$). From 57 reports of the best outcome, out of 98
subjects, they calculate a lying rate of 49.68%, with a 95% CI of (45.3%, 53.95%). Using the
Bayesian method with a uniform prior, the confidence interval becomes (`r bennd_bounds[1]`, 
`r bennd_bounds[2]`), about twice as big.

@banerjee2018spillover use the GSV method to estimate confidence intervals for proportion of liars
in a die roll task. They estimate the proportion of liars who report a die roll above 3 ($P = 0.5$),
for several treatments. Table \ref{tab:banerjee-recalc} in the appendix shows GSV confidence
intervals, along with recalculated Bayesian confidence intervals (from a uniform prior), and
confidence intervals for the difference between lying to the "Same" and "Other" caste. The Bayesian
confidence intervals are much larger than GSV confidence intervals. Only a couple of significant
results survive. (Note that significance tests in the original paper were done with standard
frequentist techniques, not the GSV method.) More importantly, the N is rather low
to make useful inferences about the differences between groups. For example, for the T2-winners-GC
group in the "aligned payoffs" treatment, differences in lying could be as much as 40% in either
direction.

@hugh2016honesty estimates the dishonesty rates of 15 nations using a coin flip experiment. I use
empirical Bayes to check these results. For my prior over $\lambda$, I fit a beta distribution
using the 15 observations of *2R/N - 1*. I then updated this prior separately for each country to
find new confidence intervals and point estimates of the means.^[Results available on request.]
There is some "shrinkage" towards the pooled mean from the naïve per-country estimates found by
calculating *2R/N - 1* separately for each country. One of the strengths of empirical Bayes, as
@casella1985introduction points out, is that it "anticipates regression to the mean". Using equation
(\ref{eqn:hypothesis-testing}), I calculated the probability of different $\lambda$ values for
each pair of countries in the data. Reassuringly, there were still significant differences between
countries.

# Software

The Bayesian methods described here are implemented in R code, available at https://github.com/hughjonesd/GSV-comment. In this section I give some simple examples of how
to use it. More details are available at the website.

To load the code, download the file "bayesian-heads-cts.R" from github, and source it in the R
command line:

```{r code-example-1, eval = FALSE, echo = TRUE}
source("bayesian-heads-cts.R")
```
